Formatting a Master's Thesis and a bunch of other things that are not really needed in here

### 2019-04-16 MScTemplateCS.tex
Fixed the title box and added commands for one, two or three lines titles.tr
Changed some of the fonts to allow for better output in Overleaf. (It's still recommended to use XeLaTeX on a local environment)
Fixed the issue with missing names on the cover, in case of two authors.
Added the list of used packages at the end of the document, before the pop-sci. To hide it, use the nofilelist option for the package.

\documentclass{cslthse-msc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}

%\geometry{showframe}
%better like this?
\student{Flavius Gruian}{Flavius.Gruian@cs.lth.se}
%\students{Flavius Gruian}{Flavius.Gruian@cs.lth.se}{Camilla Lekebjer}{Camilla.Lekebjer@cs.lth.se}

\thesisnumber{LU-CS-EX: 2019-XX} % Birger Swahn will provide this number to you, once the thesis is ready for publication
% default is Master. Uncomment the following for "kandidatarbete"/Bachelor's thesis
%\thesistype{Bachelor}

\title{Formatting a Master's Thesis}

@@

@@

>>>>

%\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}

% used to display the used files at the end. Select nofilelist as a package option to disable this
\listfiles % initialize

%\geometry{showframe}
%better like this?
%\student{Flavius Gruian}{Flavius.Gruian@cs.lth.se}
\students{Flavius Gruian}{Flavius.Gruian@cs.lth.se}{Camilla Lekebjer}{Camilla.Lekebjer@cs.lth.se}

\thesisnumber{LU-CS-EX: 2019-XX} % Birger Swahn will provide this number to you, once the thesis is ready for publication
% default is Master. Uncomment the following for "kandidatarbete"/Bachelor's thesis
%\thesistype{Bachelor}{Kandidatarbete}

%\title{Formatting a Master's Thesis}
\title{Formatting a Master's Thesis and a bunch of other things that are not really needed in here}

%\onelinetitle
%\twolinestitle
\threelinestitle
%\fourlinestitle

@@

\subsubsection{Since 2019/04/01}
\begin{itemize}
\item Added the \texttt{nofilelist} option in to the package. By default the list of packages is displayed at the end of the document, before the pop-sci. With the option, the file list is not displayed. Used mainly for debug purposes. Ignore warnings and the two errors about the \texttt{fontenc.sty}
\end{itemize}

@@

% display used packages information unless noflielist is used in the cslthse-msc package option
\printfilelist
